---
title: "Exploration of Available Spatial Data for Focal Saline Lakes"
author: "Margaux Sleckman"
#date: "`r Sys.Date()`"
output:
  html_document: default
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

```

<br>
<br>

#### Summary

The following document gathers the spatial data immediately available for the 19 focal saline lakes that will be used to conduct the salines lakes data gap analysis.   

<br>

**Spatial data gathered:** 

* Lakes polygon shapefiles

* HUC08 and HUC12 catchment boundary shapefiles associated with our selected lakes 

* Flowlines within HUC08 boundaries, as polyline shapefiles 

We reviewed three databases, querying our selected saline lakes (see table below). In addition we pulled the HUC08 and HUC12 water catchment boundaries surrounding each lake. 

|Database: | Focal Lakes Count | Use: |
| ---------|----------|---------------|
|[LAGO US LOCUS database](https://portal.edirepository.org/nis/mapbrowse?packageid=edi.854.1) | 14/19 | No
|[HydroLAKES](https://www.hydrosheds.org/products/hydrolakes) |  11/19 | No
|[National Hydrological Dataset - high res](https://www.usgs.gov/national-hydrography/nhdplus-high-resolution) - water body attributes | 18/19 (Carson sink missing) | Yes 

NHD (high resolution/non-high resolution) will be used as the data source for the majority of the spatial data of our focal saline lakes.

<br>

**Notes on specific lakes:** 

* Lake Winnemucca, NV is not available in the high resolution NHD database. Spatial data for this lake was retrieved from non-high res NHD.

* 'Warner Lake' looks to be in fact a collection chain of 12 shallow lakes in South East Oregon. This needs to be confirmed. 

* Carson Sink does not exist in any of our databases. A point location has been added to the lake map below to indicate our best estimate of the location of Carson Sink.
The spatial data for the Carson Sink must be retrieved separately.  

```{r libs, echo=FALSE, message=FALSE}

library(sf)
library(sp)
library(dplyr)
library(rgdal)         
library(readr)
library(readxl)
library(mapview)
library(rgdal)
library(RColorBrewer)
library(data.table)
library(nhdplusTools)
library(snakecase)
library(stringr)
library(kableExtra)
library(leaflet)

```

<br> 
<br>

#### Focal Saline Lakes

Lakes excel found in USGS project sharepoint folder under [Exploration/Data/Lakes_list.xlsx](https://doimspp.sharepoint.com/:x:/r/sites/IIDDStaff/_layouts/15/Doc.aspx?sourcedoc=%7BDC11027F-CD61-4240-9972-654EFEF8C401%7D&file=Lakes_list.xlsx&action=default&mobileredirect=true&cid=f49bdfe8-b10e-485c-86d0-48d02dd93a75) 

<br>

```{r get lakes from databases, include=FALSE, message = FALSE}

## CRS: keeping crs at 4326 for now
selected_crs = 4326

## List of lakes
lakes_excel <- readxl::read_xlsx('Data/Lakes_list.xlsx', col_types = 'text')

## Turning lakes into SF obj
lakes <- lakes_excel %>% 
  ## Note - lon comes first in st_as_sf()
  st_as_sf(coords = c('Lon','Lat'), crs = 4326) %>% 
  rename(Point_geometry = geometry, lake = `Lake Ecosystem`) %>% 
  mutate(State_abbr = case_when(State == 'California' ~ 'CA',
                                State == 'Nevada' ~ 'NV',
                                State == 'Utah' ~ 'UT',
                                State == 'Oregon' ~ 'OR',
                                State == 'California/Oregon' ~ 'CA',
                                TRUE ~ 'NA'),
         lake = str_to_title(lake),
         lake_w_state = paste(lake,State_abbr, sep = ','),
         lake_name_shrt = trimws(str_replace(lake,
                                             pattern = 'Lake',
                                             replacement = "")))
         
## Get huc08 for focal lakes
huc08_df <- get_huc8(AOI = lakes$Point_geometry)
huc04_comids_for_download <- substr(huc08_df$huc8, start = 1, stop = 4) %>% unique()

# States
states <- st_read('Data/statesp010g.shp_nt00938/statesp010g.shp') %>%
  filter(STATE_ABBR %in% c('CA',"NV",'UT','OR')) %>% 
  st_transform(crs = st_crs(lakes)) %>% 
  select(NAME,STATE_ABBR, geometry)

```

```{r table, echo = FALSE}

lakes %>%
  select(lake, State) %>% 
  kbl(caption = 'Selected Saline Lakes', align= 'ccc') %>%
   kable_styling(bootstrap_options = "striped",
                 full_width = F,
                 position = "center")

```

```{r nhdhr, include=FALSE}

# Note - added my local path because i had everything downloaded already
## in Download_nhd.R, nhdhr_dir is created and would overwrite mine if that script is sourced
nhdhr_dir <- 'Data/temp_hr_lakes/'

## nhdplustools download data if you have not done so.
# source('Data/Download_nhd.R')

nhd_hr <- nhdplusTools::get_nhdplushr(hr_dir = nhdhr_dir,
                                      layer= 'NHDWaterbody')

## Cleaning dataframe
nhdhr_saline_lakes <- nhd_hr$NHDWaterbody %>%
  filter(GNIS_Name %in% lakes$lake) %>%
  st_zm() %>%
  st_make_valid() %>%
  st_transform(crs = st_crs(lakes)) %>% 
  st_join(x = ., y = states) %>% 
  mutate(lake_w_state = paste(GNIS_Name, STATE_ABBR, sep = ',')) %>% 
  filter(lake_w_state %in% lakes$lake_w_state)

## Spatial group by
lakes_nhdhr <- nhdhr_saline_lakes %>%
  group_by(lake_w_state,GNIS_Name) %>%
  summarize(geometry = st_union(Shape)) %>% 
  ungroup()

```

```{r special handling, include=FALSE}

## Handling Winnemucca which does not exist in nhd hr - only nhd
Winnemucca <- get_waterbodies(AOI = st_sfc(lakes$Point_geometry[lakes$lake =='Winnemucca Lake'],
                                        crs = selected_crs))

## Handling Warner lakes/wetlands which is made u of collection of shallow wetland lakes. Full list taken from https://www.blm.gov/visit/warner-wetlands
Warner_lakes <- c('Pelican Lake',
                  'Crump Lake',
                  'Hart Lake',
                  'Anderson Lake',
                  'Swamp Lake',
                  'Mugwump Lake',
                  'Flagstaff Lake',
                  'Upper Campbell Lake',
                  'Campbell Lake',
                  'Stone Corral Lake',
                  'Turpin Lake', 
                  'Bluejoint Lake')

# there are two OR swamp lakes - id-ed the incorrect one and removed in following code chunk 
wrong_swamp_lake_id <- '142134706'

Warner <-  nhd_hr$NHDWaterbody %>% 
  filter(GNIS_Name %in% Warner_lakes,
         Permanent_Identifier != wrong_swamp_lake_id) %>% 
  st_zm() %>% 
  st_make_valid() %>%
  st_transform(crs = st_crs(lakes)) %>% 
  st_join(x = ., y = states) %>% 
  mutate(lake_w_state = paste('Warner Lake', STATE_ABBR, sep = ',')) %>% 
  filter(lake_w_state %in% lakes$lake_w_state) 

Warner_lakes <- Warner %>%
  group_by(lake_w_state) %>%
  summarize(geometry = st_union(Shape)) %>% 
  ungroup()

## Carson Sink - extracting point for map 
carson_sink <- lakes %>% filter(lake == 'Carson Sink') %>% 
  mutate(X = st_coordinates(Point_geometry)[1],
         Y = st_coordinates(Point_geometry)[2],
         lake = gsub('Sink',"Sink*",lake))

```

```{r Combining_all_lakes, echo = FALSE}

lakes_map <- lakes_nhdhr %>% 
  add_row(lake_w_state = 'Winnemucca Lake,NV',
          GNIS_Name = 'Winnemucca Lake',
          geometry = Winnemucca$geometry[1]) %>%
  filter(GNIS_Name != 'Warner Lake') %>% 
  add_row(lake_w_state = Warner_lakes$lake_w_state[1],
          GNIS_Name = 'Warner Lakes',
          geometry = Warner_lakes$geometry[1]) %>%
  mutate(X = st_coordinates(st_centroid(geometry))[,1],
         Y = st_coordinates(st_centroid(geometry))[,2]) %>% 
  mutate(flag = ifelse(GNIS_Name == 'Winnemucca Lake','nhd',
                       ifelse(GNIS_Name == 'Warner Lakes',
                              'From nhd hr. The Warner Lakes (aka Warner Wetlands) consist of 12 shallow lakes in South East Oregon, and include Pelican, Crump, Hart Lakes, among others', 'From nhd hr')))
  

```

<br>

#### Map of all 19 focal saline lakes 

```{r leaflet, echo =FALSE}

pal <- colorFactor(
  palette = c('skyblue','firebrick', 'firebrick'),
  domain = lakes_map$flag)

label_settings <- labelOptions(noHide = TRUE, direction = 'right',
                               textOnly = TRUE,
                               textsize = '9px')

## valid lakes labelled on w/ leaflet
leaflet(lakes_map) %>%
  addProviderTiles("CartoDB.VoyagerNoLabels") %>% 
  addPolygons(data = lakes_map, weight=1.5, color = 'grey', opacity = 0.3,
              fillColor = ~pal(flag), fillOpacity = 0.8,
              highlightOptions = highlightOptions(color='darkblue',weight=0.5,
                                                  bringToFront = TRUE)) %>% 
    ## adding Carson sink point
    addCircleMarkers(data = carson_sink, lng = ~X, lat = ~Y, label = ~lake, weight=1, radius = 0,5, color = 'black',
                     labelOptions = label_settings) %>% 
  addLabelOnlyMarkers(~as.numeric(X),
                      ~as.numeric(Y),
                      label =  ~GNIS_Name, 
                      labelOptions = label_settings)

```


```{r}

st_write(lakes_map, 'Data/out/saline_lakes.shp', append = FALSE)


```

*Carson Sink does not have a lake polygon.

```{r huc12 and huc8,echo =FALSE, message=FALSE, warning=FALSE}

lakes_huc12 <- get_huc12(AOI = lakes_map, buffer = 1) %>%
  select(id, huc12, name, states, geometry)

lakes_huc8 <- get_huc8(AOI = lakes_map, buffer = 1) %>%
  select(id, huc8, name, states, geometry)

huc8_flines_CA <- get_nhdplus(AOI = lakes_huc8 %>% filter(str_detect(states, 'CA')),
                              realization = 'flowline')

huc8_flines_OR <- get_nhdplus(AOI = lakes_huc8 %>% filter(str_detect(states, 'OR')),
                              realization = 'flowline')

huc8_flines_NV <- get_nhdplus(AOI = lakes_huc8 %>% filter(str_detect(states, 'NV')),
                              realization = 'flowline')

huc8_flines_UT <- get_nhdplus(AOI = lakes_huc8 %>% filter(str_detect(states, 'UT')),
                              realization = 'flowline')

all_flowlines <- rbind(huc8_flines_CA,
                       huc8_flines_OR,
                       huc8_flines_NV,
                       huc8_flines_UT)

```

<br>

#### Map of HUC08 (red) and HUC12 (green) regions surrounding focal lakes
```{r mapview_huc, echo=FALSE}

leaflet(lakes_map) %>%
  addProviderTiles("CartoDB.VoyagerNoLabels") %>% 
  addPolygons(data = lakes_map, weight=1.5, color = 'grey', opacity = 0.3,
              fillColor = 'lightblue', fillOpacity = 0.8,
              highlightOptions = highlightOptions(color='darkblue',weight=0.5, bringToFront = TRUE)) %>% 
  addPolygons(data = lakes_huc8, weight=1, color = 'red', fillColor = 'transparent') %>%   addPolygons(data = lakes_huc12, weight=1, color = 'green', fillColor = 'transparent') %>%
  addLegend("bottomright",
           colors = c('red','green','lightblue'),
           labels = c('HUC08 boundary','HUC12 boundary', 'Focal lakes'),
    title = "Legend",
    opacity = 1
  )

# mapview(lakes_huc12, col.regions = 'transparent', color = 'green')+
#   mapview(lakes_huc8, col.regions = 'transparent', color = 'red')+
#   mapview(lakes_map)

```

<br>

#### Map of HUC08 region around lakes and all HUC08 flowlines 

```{r mapview_flowlines, echo=FALSE}

leaflet(lakes_map) %>%
  addProviderTiles("CartoDB.VoyagerNoLabels") %>% 
  addPolygons(data = lakes_map, weight=1.5, color = 'grey', opacity = 0.3,
              fillColor = 'lightblue', fillOpacity = 0.8,
              highlightOptions = highlightOptions(color='darkblue',weight=0.5, bringToFront = TRUE)) %>% 
  addPolygons(data = lakes_huc8, weight=1, color = 'red', fillColor = 'transparent') %>%
  addPolylines(data = all_flowlines,  weight = 0.2, color = 'darkblue') %>% 
  addLegend("bottomright",
           colors = c('red','darkblue'), labels = c('HUC08 boundary','HUC08 flowlines'),
    title = "Legend",
    opacity = 1
  )

# mapview(all_flowlines,  color = 'lightblue')+
# mapview(lakes_huc8, col.regions = 'transparent', color = 'red') +
# mapview(lakes_map)

```
