---
title: "Exploration of Available Spatial Data for Focal Saline Lakes"
author: "Margaux Sleckman"
date: "5/20/2022"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

```

#### Context

The following report gathers the spatial data available for the 19 focal saline lakes that will be used to conduct the salines lakes data gap analysis.   

Spatial data gathered: 
 * Lakes polygon shapefiles
 * HUC08 and HUC12 catchment boundary shapefiles  
 * Flowlines within huc 8 boundary associated with lake, as polyline shapefiles 

We review three databases and queried to our selected saline lakes. In addition we pulled the huc8 and huc 12 catchments surrounding each lake. 

|Database: | Focal Lakes Count | Use: |
| ---------|----------|---------------|
|[LAGO US LOCUS database](https://portal.edirepository.org/nis/mapbrowse?packageid=edi.854.1) | 14/19 | No
|
|[HydroLAKES](https://www.hydrosheds.org/products/hydrolakes) |  11/19 | No
|
|[National Hydrological Dataset - high res](https://www.usgs.gov/national-hydrography/nhdplus-high-resolution) - water body attributes | 18/19 (Carson sink missing) | Yes 

Notes on specific lakes: 

* Lake Winnemucca NV was not available in high resolution NHD database. Lake spatial data was retrieved from non-high res.
* Warner Lake looks to be in fact a collection of shallow lakes  
* Carson Sink - does not exist in any of our database Will added to the list of lakes fetched from NHD

#### Libraries
```{r libs, echo=FALSE, message=FALSE}

library(sf)
library(sp)
library(dplyr)
library(rgdal)         
library(readr)
library(readxl)
library(mapview)
library(rgdal)
library(RColorBrewer)
library(data.table)
library(nhdplusTools)
library(snakecase)
library(stringr)
library(kableExtra)
library(leaflet)

```

### Set Up

Lakes excel found in sharepoint folder under [Exploration/Data/Lakes_list.xlsx](https://doimspp.sharepoint.com/:x:/r/sites/IIDDStaff/_layouts/15/Doc.aspx?sourcedoc=%7BDC11027F-CD61-4240-9972-654EFEF8C401%7D&file=Lakes_list.xlsx&action=default&mobileredirect=true&cid=f49bdfe8-b10e-485c-86d0-48d02dd93a75) 

```{r get lakes from databases, include=FALSE, message = FALSE}

## CRS: keeping crs at 4326 for now
selected_crs = 4326

## List of lakes
lakes_excel <- readxl::read_xlsx('Data/Lakes_list.xlsx', col_types = 'text')

## Turning lakes into SF obj
lakes <- lakes_excel %>% 
  ## Note - lon comes first in st_as_sf()
  st_as_sf(coords = c('Lon','Lat'), crs = 4326) %>% 
  rename(Point_geometry = geometry, lake = `Lake Ecosystem`) %>% 
  mutate(State_abbr = case_when(State == 'California' ~ 'CA',
                                State == 'Nevada' ~ 'NV',
                                State == 'Utah' ~ 'UT',
                                State == 'Oregon' ~ 'OR',
                                State == 'California/Oregon' ~ 'CA',
                                TRUE ~ 'NA'),
         lake = str_to_title(lake),
         lake_w_state = paste(lake,State_abbr, sep = ','),
         lake_name_shrt = trimws(str_replace(lake,
                                             pattern = 'Lake',
                                             replacement = "")))
         
## Get huc08 for focal lakes
huc08_df <- get_huc8(AOI = lakes$Point_geometry)
huc04_comids_for_download <- substr(huc08_df$huc8, start = 1, stop = 4) %>% unique()

## Define temp dir in data folder
nhdhr_dir <- file.path('Data', "nhdhr_lakes")

# States
states <- st_read('Data/statesp010g.shp_nt00938/statesp010g.shp') %>%
  filter(STATE_ABBR %in% c('CA',"NV",'UT','OR')) %>% 
  st_transform(crs = st_crs(lakes)) %>% 
  select(NAME,STATE_ABBR, geometry)

```

##### Focal Saline Lakes

```{r table, echo = FALSE}

lakes %>%
  select(lake, State) %>% 
  kbl(caption = 'Selected Saline Lakes') %>%
   kable_styling(bootstrap_options = "striped",
                 full_width = F,
                 position = "center")

```

```{r nhdhr, include=FALSE}

# ## nhdplustools download data if you have not done so.
# source('Data/Download_nhd.R')
nhd_hr <- nhdplusTools::get_nhdplushr(hr_dir = 'Data/temp_hr_lakes/',
                                      layer= 'NHDWaterbody')

nhdhr_saline_lakes <- nhd_hr$NHDWaterbody %>%
  filter(GNIS_Name %in% lakes$lake) %>%
  st_zm() %>%
  st_make_valid() %>%
  st_transform(crs = st_crs(lakes)) %>% 
  st_join(x = ., y = states) %>% 
  mutate(lake_w_state = paste(GNIS_Name, STATE_ABBR, sep = ',')) %>% 
  filter(lake_w_state %in% lakes$lake_w_state)

lakes_nhdhr <- nhdhr_saline_lakes %>%
  group_by(lake_w_state,GNIS_Name) %>%
  summarize(geometry = st_union(Shape)) %>% 
  ungroup()

```

```{r special handling, include=FALSE}

## Handling Winnemucca which does not exist in nhd hr - only nhd
Winnemucca <- get_waterbodies(AOI = st_sfc(lakes$Point_geometry[lakes$lake =='Winnemucca Lake'],
                                        crs = selected_crs))

## Handling Warner lakes/wetland which is a collection of lakes
Warner_lakes <- c('Pelican Lake',
                  'Crump Lake',
                  'Hart Lake',
                  'Anderson Lake',
                  'Swamp Lake',
                  'Mugwump Lake',
                  'Flagstaff Lake',
                  'Upper Campbell Lake',
                  'Campbell Lake',
                  'Stone Corral Lake',
                  'Turpin Lake', 
                  'Bluejoint Lake')

# there are two OR swamp lakes - id-ed the incorrect one and removed in following code chunk 
wrong_swamp_lake_id <- '142134706'

Warner <-  nhd_hr$NHDWaterbody %>% 
  filter(GNIS_Name %in% Warner_lakes,
         Permanent_Identifier != wrong_swamp_lake_id) %>% 
  st_zm() %>% 
  st_make_valid() %>%
  st_transform(crs = st_crs(lakes)) %>% 
  st_join(x = ., y = states) %>% 
  mutate(lake_w_state = paste('Warner Lake', STATE_ABBR, sep = ',')) %>% 
  filter(lake_w_state %in% lakes$lake_w_state) 

Warner_lakes <- Warner %>%
  group_by(lake_w_state) %>%
  summarize(geometry = st_union(Shape)) %>% 
  ungroup()

## Carson Sink - extracting point for map 
carson_sink <- lakes %>% filter(lake == 'Carson Sink') %>% 
  mutate(X = st_coordinates(Point_geometry)[1],
         Y = st_coordinates(Point_geometry)[2])

```

```{r Combining_all_lakes}

lakes_map <- lakes_nhdhr %>% 
  add_row(lake_w_state = 'Winnemucca Lake,NV',
          GNIS_Name = 'Winnemucca Lake',
          geometry = Winnemucca$geometry[1]) %>%
  filter(GNIS_Name != 'Warner Lake') %>% 
  add_row(lake_w_state = Warner_lakes$lake_w_state[1],
          GNIS_Name = 'Warner Lakes',
          geometry = Warner_lakes$geometry[1]) %>%
  mutate(X = st_coordinates(st_centroid(geometry))[,1],
         Y = st_coordinates(st_centroid(geometry))[,2]) %>% 
  mutate(flag = ifelse(GNIS_Name == 'Winnemucca Lake','nhd',
                       ifelse(GNIS_Name == 'Warner Lakes',
                              'From nhd hr. Warner lakes Wetlands consists of 12 shallow lakes in south least region of oregon, and includes Pelican, Crump, Hart Lakes, among others', 'From nhd hr')))

```


```{r leaflet, echo =FALSE}

pal <- colorFactor(
  palette = c('skyblue','firebrick', 'firebrick'),
  domain = lakes_map$flag)

label_settings <- labelOptions(noHide = TRUE, direction = 'right',
                               textOnly = TRUE,
                               textsize = '6px')

## valid lakes labelled on w/ leaflet
leaflet(lakes_map) %>%
  addProviderTiles("CartoDB.VoyagerNoLabels") %>% 
  addPolygons(data = lakes_map, weight=1.5, color = 'grey', opacity = 0.3,
              fillColor = ~pal(flag), fillOpacity = 0.8,
              highlightOptions = highlightOptions(color='darkblue',weight=0.5,
                                                  bringToFront = TRUE)) %>% 
    ## adding Carson sink point
    addCircleMarkers(data = carson_sink, lng = ~X, lat = ~Y, label = ~lake, weight=1, radius = 0,5, color = 'black',
                     labelOptions = label_settings) %>% 
  addLabelOnlyMarkers(~as.numeric(X),
                      ~as.numeric(Y),
                      label =  ~GNIS_Name, 
                      labelOptions = label_settings)

```

```{r huc12 and huc8}

lakes_huc12 <- get_huc12(AOI = lakes_map, buffer = 1) %>% 
  select(id, huc12, name, states, geometry)

lakes_huc8 <- get_huc8(AOI = lakes_map, buffer = 1) %>% 
  select(id, huc8, name, states, geometry)

huc8_flines_CA <- get_nhdplus(AOI = lakes_huc8 %>%
                                filter(str_detect(states, 'CA')),
                              realization = 'flowline')

huc8_flines_OR <- get_nhdplus(AOI = lakes_huc8 %>%
                                filter(str_detect(states, 'OR')),
                              realization = 'flowline')

huc8_flines_NV <- get_nhdplus(AOI = lakes_huc8 %>%
                                filter(str_detect(states, 'NV')),
                              realization = 'flowline')

huc8_flines_UT <- get_nhdplus(AOI = lakes_huc8 %>%
                                filter(str_detect(states, 'UT')),
                              realization = 'flowline')

all_flowlines <- rbind(huc8_flines_CA,
                       huc8_flines_OR, 
                       huc8_flines_NV,
                       huc8_flines_UT)


mapview(lakes_huc12, col.regions = 'transparent', color = 'red')
mapview(lakes_huc8, col.regions = 'transparent', color = 'green')+

mapview(huc8_flines)

```

